Comparing R packages for calculation of persistent homology

### 2020-03-19 tdabench-paper/tdabench.Rmd
updated complex labels
updated phrasing

\section{Discussion}
As persistent homology calculations continue to become a more popular tool to analyze complex multidimensional data, it will be important to understand from a computational perspective which method to use. 
In this paper, we examined two forms of persistent homology complexes: Vietoris Rips and Alpha complexes. 
Both algorithms describe the topological features through the generation of simplicial complexes. 
The advantage in saving computational time in choosing a particular algorithm depends on the point cloud characteristics.

>>>>

\section{Discussion}
As persistent homology calculations continue to become a more popular tool to analyze complex multidimensional data, it will be important to understand from a computational perspective which method to use. 
In this paper, we examined two forms of persistent homology complexes: Vietoris-Rips and alpha complexes. 
Both algorithms describe topological features through the generation of simplicial complexes. 
The advantage in saving computational time in choosing a particular algorithm depends on the point cloud characteristics.
